% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage[none]{hyphenat}
\usepackage{contact}
\usepackage{enumitem}
\voffset -20pt
\textheight = 760pt
\newcommand\oindent{0em}
\newcommand\lindent{1.5em}
\newcommand\spacing{0.6em}
\newcommand\si{\item[]}
\newenvironment{secretlist}[1]{\begin{itemize}[noitemsep,leftmargin=#1,nolistsep]}{\end{itemize}}

\begin{document}
    \name{Daniel Hertz}
    % \address used twice to have two lines of address
    % Hide my contact info from evil recruiters
    \address{\addr}
    \address{\email / \phone}

    \begin{resume}
        \section{EXPERIENCE}
            \begin{secretlist}{\oindent}
                \si \textbf{Software Engineer} \hfill Summer 2014 - Present
                \si Akamai Technologies, Cambridge, MA/London, UK (Remote)
                \si Python, SQL, Java, Perl, Javascript
                \begin{secretlist}{\lindent}
                    \si Owned and maintained mission critical legacy applications, enabling new software to be packed and distributed globally to 200,000+ machines over the CDN.
                    \si Collaborated with senior engineers on a multiple-client to multiple-server application to manage software and configuration versions, states and deployments across all machines.
                    \si Created new web-application for tracking and displaying statistics in response to internal customer need for more visibility into systems.
                    \si Maintained miscellaneous small tools in various programming languages.
                \end{secretlist}
            \end{secretlist}
            \vspace{\spacing}
            \begin{secretlist}{\oindent}
                \si \textbf{AkaPi - Digital Noticeboard Project} \hfill 2015 - Present
                \si For Raspberry Pi \& Adafruit Display Modules --- Nim, C++, Python
                \begin{secretlist}{\lindent}
                    \si Made digital noticeboard for office announcements using panels similar to ones used in outside advertisements (such as in Times Square). Aggregates data from APIs such as Twitter and forcast.io to display weather infomation, internal traffic statistics, stock performance, upcoming bus and train times and cute animations.
                    \si This project also required multiple contributions to the open source language Nim, as a result of its relative immaturity.
                \end{secretlist}
            \end{secretlist}
            \vspace{\spacing}
            \begin{secretlist}{\oindent}
                \si \textbf{Maypole - A Collaborative Video Creator} \hfill 2014
                \si Final Year Project, Imperial College, London --- Objective-C, Python
                \begin{secretlist}{\lindent}
                    \si Created iPhone application to produce a crowd-sourced video of any event, using multiple video streams from different devices.
                    \si The application utilised a distributed back end system, based in Amazon Web Services, to sync timestamps and audio and create a single video from the multiple sources.
                \end{secretlist}
            \end{secretlist}
            \vspace{\spacing}
            \begin{secretlist}{\oindent}
                \si \textbf{Video Encoding Intern} \hfill Summer 2013
                \si Akamai Technologies, San Diego, CA --- Python, Javascript
                \begin{secretlist}{\lindent}
                    \si Ensured reliability in a distributed data store using CouchDB.
                    \si Investigated and produced a report on new features for the transcoding product.
                \end{secretlist}
            \end{secretlist}
            \vspace{\spacing}
            \begin{secretlist}{\oindent}
                \si \textbf{Pebble Watchfaces} \hfill Spring 2012
                \si For Pebble's beta SDK --- C, Javascript, HTML
                \begin{secretlist}{\lindent}
                    \si Produced embedded apps for the most popular smartwatch at the time using the C-based SDK. Users installed the applications over 4000 times.
                \end{secretlist}
            \end{secretlist}
            \vspace{\spacing}
            \begin{secretlist}{\oindent}
                \si \textbf{Software Intern} \hfill Summer 2012
                \si Akamai Technologies, Cambridge, MA --- Java, Perl
                \begin{secretlist}{\lindent}
                    \si Improved several internal web-applications for managing all of the deployed Akamai machines.
                \end{secretlist}
            \end{secretlist}
            \vspace{0.6em}
            \begin{secretlist}{\oindent}
                \si \textbf{Youth Worker} \hfill 2009 - 2014
                \si Kew Youth Club, West London, UK
                \begin{secretlist}{\lindent}
                    \si Worked to provide a supervised space for 12 - 15 year olds to come and socialise.
                \end{secretlist}
            \end{secretlist}

        \section{EDUCATION}
            \begin{secretlist}{\oindent}
                \si \textbf{Bachelor of Engineering}, Computing
                \si First Class Honours, 2014
                \si Imperial College London
            \end{secretlist}

        \section{SEMI-RELEVANT PERSONAL INFO}
            \begin{secretlist}{\oindent}
                \si \textbf{Dual Citizen}, United States of America and the United Kingdom
                \si \textbf{Founder and President 2013-2014}, Imperial College London LEGO Society
                \si \textbf{Founder}, Pirate Party UK, a political party registered in the United Kingdom to fight to protect citizens' digital rights
            \end{secretlist}

        \section{BUZZWORD SOUP}
            \begin{secretlist}{\oindent}
                \si \textbf{Languages:} Bash/Sh, CSS, HTML, Javascript, Python, Java, Perl, SQL
                \si \textbf{Operating Systems:} macOS, Ubuntu (Linux)
                \si \textbf{Other Software/Skills:} D3.js, git, intelliJ, JIRA, jQuery, \LaTeX, GNU Make, Perforce, POSIX shell, PosgreSQL, Vim
            \end{secretlist}
    \end{resume}
\end{document}